\pkg{Rgbp}: An \proglang{R} Package for Conjugate Gaussian, Poisson, and Binomial Hierarchical Modeling and Frequency Method Checking on Overdispersed Data

### 2015-06-10 jss/article_v2.tex
any change?

Similarly, the likelihood function of $r$ for the Poisson hierarchical model  comes from the independent Negative-Binomial marginal distributions of the observed data with the random effects, $\lambda_1, \lambda_2, \ldots, \lambda_k$, integrated out;
\begin{equation}\label{marginal_poisson}
L_p(r)=\prod_{j=1}^k f(y_j\vert r)=\prod^{k}_{j=1} \frac{\Gamma(r \lambda^E+y_j)}{\Gamma(r\lambda^E)(y_j!)}(1-B_{j})^{y_{i}}B_{j}^{r \lambda^E},
\end{equation}
where $\Gamma(a)$ is a gamma function defined as $\int_0^\infty x^{a-1}e^{x}dx$ for a positive constant $a$. The posterior density function of $r$, $f(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in Equation \ref{marginal_poisson} times the hyper-prior density function of $r$, $dr/r^2$;
\begin{equation}\label{marginal_post_poisson}
f(r \vert \boldsymbol{y})\propto L_p(r)dr/r^2.
\end{equation}

@@

Overall, obtaining point and interval estimates of each random effect is our primary inferential interest.  The approximate Bayesian tool assumes that the unconditional posterior distribution of each random effect follows a skewed-Normal distribution for the Gaussian case,  a Beta distribution for the Binomial case, or a Gamma distribution for the Poisson case, whose parameters are matched to the estimated unconditional posterior moments of each random effect. We use these assumed unconditional posterior distributions to make point and interval estimates of each random effect.

@@

Estimating the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$ ($B_j\equiv V_j/(V_j+A)$ for the Gaussian model) and the conditional posterior moments of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ ($\mu^E_1, \mu^E_2, \ldots, \mu^E_k$ for the Gaussian model or $\lambda^E$ for the Poisson model), is the main estimation problem for the  models that \code{gbp} assumes. This is because these moment estimates are used to estimate the unconditional posterior moments of the random effects, $p_1, p_2, \ldots, p_k$ ($\mu_1, \mu_2, \ldots, \mu_k$ for the Gaussian model or $\lambda_1, \lambda_2, \ldots, \lambda_k$ for the Poisson model). Taking the Binomial model as an example, with the assumption that hyper-parameters $r$ and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ are
\begin{eqnarray}
E(p_{j}\vert \boldsymbol{y}) &=&E(E(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})E(p^E_{j}\vert  \boldsymbol{y})\label{postmean} \\
~~~~~~Var(p_{j}\vert \boldsymbol{y}) &=&  E(Var(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})+Var(E(p_{j}\vert r, \boldsymbol{\beta},\boldsymbol{y})\vert \boldsymbol{y})\label{postvar}\\
&=& E\big(p^{\ast}_{j}(1-p^{\ast}_{j})/ (r+n_{j}+1)\vert  \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big) \\
&\approx&E\big(p^{\ast}_{j}(1-p^{\ast}_{j})(1-\textrm{B}_{j})/n_{i}\vert \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big)\\
&=&h_b(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}), E(B^3_j\vert\boldsymbol{y}),  E(p^E_{j}\vert\boldsymbol{y}), E((p^E_{j})^2\vert\boldsymbol{y})).\label{approximate_var}
\end{eqnarray}
Note that the unconditional posterior mean and approximate variance of random effect $j$ in Equation \ref{postmean}  and \ref{approximate_var}  are functions of the unconditional posterior moments of shrinkage factors and expected random effects. We specify the function $h_b$  in Appendix \ref{apppostvar}.

We assumed that hyper-parameters $r$ ($A$ for the Gaussian model) and  $\boldsymbol{\beta}$ were independent a posteriori for the Binomial model, considering that they are independent a posteriori in the limit of $k$ going to infinity  because they are asymptotically Normally distributed. Also, \cite{morris1997}  empirically showed that their covariance from the observed information matrix of the Poisson model, though with a different parametrization, was close to 0 in a small sample setting. 
%For the Gaussian model we do not assume the posterior independence between $A$ and $\boldsymbol{\beta}$ because the conditional posterior variance of the random effect is a constant function of the conditional posterior mean, which is much simpler than that of the Binomial model.

@@

Considering that Equation \ref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on a logarithmic scale of $r$, i.e., $\alpha=-\log(r)$ (or $\alpha=\log(A)$ for the Gaussian model), because the distribution of $\alpha$ is more symmetric than that of $r$ and $\alpha$ is defined on a real line without any boundary issues. Since $A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto e^\alpha L(\alpha)$, the estimated posterior mean in Equation \ref{admmean} is 
\begin{equation}\label{meaninvariance}
\hat{B}^\ast_j=\frac{e^{-\hat{\alpha}}}{n_j+e^{-\hat{\alpha}}},
\end{equation}

@@

We need the invariance information introduced in \cite{tang2011} to estimate the variance in Equation \ref{admvar}, which is defined as 
\begin{eqnarray}
\textrm{inv.info} &\equiv& -\frac{d^2 \log(A(B_j\vert \boldsymbol{y}))}{d[logit(B_j)]^2}\bigg\vert_{B_j=\hat{B}^\ast_j}=-\frac{d^2 \log(A(B_j(r)\vert \boldsymbol{y}))}{d[\log(r)]^2}\bigg\vert_{r=\hat{r}}\label{invariance}\\
&=& -\frac{d^2 \log(A(B_j(r(\alpha))\vert \boldsymbol{y}))}{d\alpha^2}\bigg\vert_{\alpha=\hat{\alpha}}\nonumber
\end{eqnarray}

Note that this invariance information is  the negative Hessian value of $\alpha+\log(L(\alpha))$ at the mode $\hat{\alpha}$. Using the invariance information, we  estimate the posterior variance in Equation \ref{admvar} as
\begin{equation}\label{varianceinvariance}
\widehat{Var}(B_j\vert\boldsymbol{y})=\frac{\hat{B}^{\ast2}_j(1-\hat{B}^\ast_j)^2}{inv.info +\hat{B}^\ast_j(1-\hat{B}^\ast_j)}.
\end{equation}

@@

\subsubsection{Unconditional posterior moments of expected random effects}
The Gaussian and Binomial models need to estimate the unconditional posterior moments of expected random effects. We estimate them using their relationship to the conditional posterior moments. For a non-negative constant $c$, the unconditional posterior moments are
\begin{equation}
E((\mu^E_j)^c\vert\boldsymbol{y})=E(E((\mu^E_j)^c\vert A, \boldsymbol{y})\vert\boldsymbol{y})~~\textrm{and}~~E((p^E_j)^c\vert\boldsymbol{y})=E(E((p^E_j)^c\vert r, \boldsymbol{y})\vert\boldsymbol{y}).
\end{equation}
We use the ADM to estimate the conditional expectations inside, and plug-in $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ to estimate the outer unconditional expectations.
%We estimate the unconditional posterior moments by the estimated conditional posterior moments that we obtain from the conditional posterior distribution of $\mu^E_j\vert A, \boldsymbol{y}$ or that of $p^E_j\vert r, \boldsymbol{y}$ with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in.

To be specific, the ADM for the Binomial model assumes that the conditional posterior distribution of each expected random effect given $\hat{\alpha}$ follows a Beta distribution  because the moment calculation of the expected random effects ($p^E_{1}, p^E_{2}, \ldots p^E_{k}$) involves an intractable integration.  For example, the first conditional posterior moment is
\begin{equation}\label{priormoment1}
E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{e^{x_j^\top\boldsymbol{\beta}}}{1+e^{x_j^\top\boldsymbol{\beta}}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{e^{x_j^\top\boldsymbol{\beta}}}{1+e^{x_j^\top\boldsymbol{\beta}}}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\boldsymbol{\beta}.
\end{equation}
%We estimate the assumed Beta distribution using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$. We estimate the conditional posterior moments of the expected random effects and treat them as their estimated unconditional posterior moments obtained by the (Laplace) approximate marginal likelihood function of $\boldsymbol{\beta}$.
% The conditional and unconditional posterior moment estimates are almost identical due to the small covariance between $r$ and $\boldsymbol{\beta}$ in the observed information matrix. In addition, calculating the conditional posterior moments is computationally less burdensome. 
%Considering that the expected random effects are a function of logistic regression coefficients $\boldsymbol{\beta}$, we can use the Delta method for the asymptotic Normal distribution of $p^E_{j}(\hat{\boldsymbol{\beta}}_{MLE})$. However, the Normal approximation goes through the same support and boundary issues as the shrinkage factors do. Instead, the ADM assumes that the conditional posterior distribution of $p^E_{j}(\boldsymbol{\beta})$ follows a Beta distribution, using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$.

We assume the conditional posterior distribution of expected random effect $j$ is a Beta distribution as follows;
\begin{equation}\label{admpriormean}
p^E_{j}\vert\hat{\alpha}, \boldsymbol{y}=\frac{e^{x_j^\top\boldsymbol{\beta}}}{1+e^{x_j^\top\boldsymbol{\beta}}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\sim \textrm{Beta}(b_{1j}, b_{0j})\sim \frac{G(b_{1j})}{G(b_{1j})+G(b_{0j})},
\end{equation}

where $G(b_{1j})$ is a random variable following a Gamma$(b_{1j}, 1)$ distribution with a unit scale and independently $G(b_{0j})$ has a Gamma($b_{0j}, 1)$ distribution.  Note that the representation in Equation \ref{admpriormean} is equivalent to saying $e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables. Its mean and variance are
\begin{eqnarray}
E(e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y})&=&E\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{b_{1j}}{b_{0j}-1}\equiv\eta_j,\label{priormean1}\\
~~~~~Var(e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y})&=&Var\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{\eta_j(1+\eta_j)}{b_{0j}-2}.\label{priorvariance1}
\end{eqnarray}

In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$ follows Normal$[\hat{\beta}, \hat{\Sigma}]$, where $\hat{\boldsymbol{\beta}}$ is the mode of $p(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode. Thus, the posterior distribution of $x_j^\top\boldsymbol{\beta}$ is also Normal with mean $x_j^\top\hat{\boldsymbol{\beta}}$ and variance $x_j^\top\hat{\Sigma} x_j$.

Using the property of the log-Normal distribution for $\exp(x_j^\top\boldsymbol{\beta})$, we get the numerical values of the posterior mean and variance in Equation \ref{priormean1} and \ref{priorvariance1} as
\begin{eqnarray}
\eta_j&=&e^{x_j^\top\hat{\boldsymbol{\beta}}+x_j^\top\hat{\Sigma} x_j/2},\label{priormean2}\\
~~~~~\widehat{Var}(e^{x_j^\top\boldsymbol{\beta}}\vert\boldsymbol{y})&=&\eta^2_j\big(e^{x_j^{T}\hat{\Sigma} x_j}-1\big).\label{priorvariance2}
\end{eqnarray}

By matching the  mean and variance in Equation \ref{priormean2} and \ref{priorvariance2} to $b_{1j}$ and $b_{0j}$ in Equation \ref{priormean1} and \ref{priorvariance1}, we obtain the values of $b_{1j}$ and $b_{0j}$ as follows;
\begin{equation}\label{priormeanpara}
b_{1j}=\eta_j+\frac{\eta_j + 1}{e^{x_j^{T}\hat{\Sigma} x_j}-1}~~\textrm{and}~~b_{0j}=\frac{\eta_j + 1}{\eta_j(e^{x_j^{T}\hat{\Sigma} x_j}-1)}+2.
\end{equation}

Finally we estimate the unconditional posterior moments of the expected random effects, $E((p^E_{j})^c\vert\boldsymbol{y})$, by $E((p^E_{j})^c\vert\hat{\alpha}, \boldsymbol{y})=B(b_{1j} + c, b_{0j})/B(b_{1j}, b_{0j})$ for $c\ge0$.
%\begin{equation}\label{priormeanmoments}
%\widehat{E}((p^E_{j})^c\vert\boldsymbol{y})= \frac{B(\hat{b}_{1j} + c, \hat{b}_{0j})}{B(\hat{b}_{1j}, \hat{b}_{0j})}.
%\end{equation}

@@

\subsection{Estimation for random effects}
It is intractable to derive analytically the unconditional posterior distribution of each random effect  for our three models, which motivates us to assume again that each random effect has a skewed Normal distribution \citep{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
\begin{eqnarray}
\mu_j\vert\boldsymbol{y} &\sim& \textrm{skewed-Normal}(\phi, \omega, \delta),\label{skewnormal}\\
p_j\vert \boldsymbol{y} &\sim& \textrm{Beta}(t_{1j}, t_{0j}),\label{betapost}\\
\lambda_j\vert \boldsymbol{y} &\sim& \textrm{Gamma}(s_{1j}, s_{0j}).\label{gammapost}
\end{eqnarray}

\cite{kelly2014advances}  matches the  three estimated unconditional posterior  moments of the random effects to the three parameters $(\phi, \omega, \delta$) of the skewed-Normal distribution in Equation \ref{skewnormal}, i.e., location parameter $\phi$, scale parameter $\omega$, and a skewness parameter $\delta$. (Hey Joey, could you add a brief description about how to match moments?) \cite{kelly2014advances} also shows that the skewed-Normal approximation improves a Normal approximation \citep{tang2011, morris2012} in terms of the frequency properties   of random effects.

@@

 For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimated unconditional posterior mean and variance, respectively, with the estimated unconditional posterior moments of shrinkage factors plugged-in to Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}. The estimates of the two parameters $s_{1j}$ and $s_{0j}$ in Equation \ref{gammapost} are
\begin{equation}\label{posttrueprob}
\hat{s}_{1j}=\frac{\hat{\mu}_{\lambda_j}^2}{\hat{\sigma}^2_{\lambda_j}},~\textrm{and}~~\hat{s}_{0j}=\frac{\hat{\mu}_{\lambda_j}}{\hat{\sigma}^2_{\lambda_j}}.
\end{equation}

Finally, the approximate unconditional posterior distribution of random effect $j$ for the Binomial model is
\begin{equation}\label{trueapprox}
p_j\vert \boldsymbol{y} \stackrel{.}{\sim} \textrm{Beta}(\hat{t}_{1j}, \hat{t}_{0j}),
\end{equation}
and that for the Poisson model is
\begin{equation}\label{trueapprox_poisson}
\lambda_j\vert \boldsymbol{y} \stackrel{.}{\sim} \textrm{Gamma}(\hat{s}_{1j}, \hat{s}_{0j}).
\end{equation}

>>>>

Similarly, the likelihood function of $r$ for the Poisson hierarchical model  comes from the independent Negative-Binomial marginal distributions of the observed data with the random effects, $\lambda_1, \lambda_2, \ldots, \lambda_k$, integrated out;
\begin{equation}\label{marginal_poisson}
L_p(r)=\prod_{j=1}^k f(y_j\vert r)=\prod^{k}_{j=1} \frac{\Gamma(r \lambda^E+y_j)}{\Gamma(r\lambda^E)(y_j!)}(1-B_{j})^{y_{i}}B_{j}^{r \lambda^E},
\end{equation}
where $\Gamma(a)$ is a gamma function defined as $\int_0^\infty x^{a-1}\exp(x)dx$ for a positive constant $a$. The posterior density function of $r$, $f(r\vert \boldsymbol{y})$, for the Poisson hierarchical model is  the likelihood function in Equation \ref{marginal_poisson} times the hyper-prior density function of $r$, $dr/r^2$;
\begin{equation}\label{marginal_post_poisson}
f(r \vert \boldsymbol{y})\propto L_p(r)dr/r^2.
\end{equation}

@@

Overall, obtaining point and interval estimates of each random effect is our primary inferential interest.  The approximate Bayesian tool assumes that the unconditional posterior distribution of each random effect, such as $\mu_j\vert\boldsymbol{y}$, $p_j\vert\boldsymbol{y}$, or $\lambda_j\vert\boldsymbol{y}$,  follows a skewed-Normal distribution for the Gaussian case,  a Beta distribution for the Binomial case, or a Gamma distribution for the Poisson case. We match the parameters of the assumed distribution to the estimated unconditional posterior moments of each random effect, $\hat{E}(\mu_j^c\vert\boldsymbol{y}$), $\hat{E}(p_j^c\vert\boldsymbol{y}$), or $\hat{E}(\lambda_j^c\vert\boldsymbol{y}$) for a non-negative constant $c$. We use these assumed unconditional posterior distributions to make point and interval estimates of each random effect.

@@

Estimating the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$ (or $B_j\equiv V_j/(V_j+A)$ for the Gaussian model) and the conditional posterior moments of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ ($\mu^E_1, \mu^E_2, \ldots, \mu^E_k$ for the Gaussian model or $\lambda^E$ for the Poisson model), is the main estimation problem for the  models that \code{gbp} assumes. This is because we use these moment estimates to estimate the unconditional posterior moments of the random effects, $E(\mu_j^c\vert\boldsymbol{y}$), $E(p_j^c\vert\boldsymbol{y}$), or $E(\lambda_j^c\vert\boldsymbol{y}$) for a non-negative constant $c$. Taking the Binomial model as an example, with the assumption that hyper-parameters $r$ and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ are
\begin{eqnarray}
E(p_{j}\vert \boldsymbol{y}) &=&E(E(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})E(p^E_{j}\vert  \boldsymbol{y})\label{postmean} \\
~~~~~~Var(p_{j}\vert \boldsymbol{y}) &=&  E(Var(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})+Var(E(p_{j}\vert r, \boldsymbol{\beta},\boldsymbol{y})\vert \boldsymbol{y})\label{postvar}\\
&=& E\big(p^{\ast}_{j}(1-p^{\ast}_{j})/ (r+n_{j}+1)\vert  \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big) \\
&\approx&E\big(p^{\ast}_{j}(1-p^{\ast}_{j})(1-\textrm{B}_{j})/n_{i}\vert \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big)\\
&=&h_b(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}), E(B^3_j\vert\boldsymbol{y}),  E(p^E_{j}\vert\boldsymbol{y}), E((p^E_{j})^2\vert\boldsymbol{y})).\label{approximate_var}
\end{eqnarray}
Note that the unconditional posterior mean and approximate variance of random effect $j$ in Equation \ref{postmean}  and \ref{approximate_var}  are functions of the unconditional posterior moments of shrinkage factors and expected random effects. We specify the function $h_b$  in Appendix \ref{apppostvar}.

We assume that hyper-parameters $r$ ($A$ for the Gaussian model) and  $\boldsymbol{\beta}$ are independent a posteriori for the Binomial model. This is because in the limit of $k$ going to infinity  they are asymptotically Normally distributed, and \cite{morris1997}  empirically showed that their covariance from the observed information matrix of the Poisson model, though with a different parametrization, was close to 0 in a small sample setting. 
%For the Gaussian model we do not assume the posterior independence between $A$ and $\boldsymbol{\beta}$ because the conditional posterior variance of the random effect is a constant function of the conditional posterior mean, which is much simpler than that of the Binomial model.

@@

Considering that Equation \ref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on a logarithmic scale of $r$, i.e., $\alpha=-\log(r)$ (or $\alpha=\log(A)$ for the Gaussian model), because the distribution of $\alpha$ is more symmetric than that of $r$ and $\alpha$ is defined on a real line without any boundary issues. Since $A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto \exp(\alpha) L(\alpha)$, the estimated posterior mean in Equation \ref{admmean} is 
\begin{equation}\label{meaninvariance}
\hat{B}^\ast_j=\frac{\exp(-\hat{\alpha})}{n_j+\exp(-\hat{\alpha})},
\end{equation}

@@

We need  invariance information introduced in \cite{tang2011} to estimate the variance in Equation \ref{admvar}, which is defined as 
\begin{eqnarray}
\textrm{inv.info} &\equiv& -\frac{d^2 \log(A(B_j\vert \boldsymbol{y}))}{d[logit(B_j)]^2}\bigg\vert_{B_j=\hat{B}^\ast_j}=-\frac{d^2 \log(A(B_j(r)\vert \boldsymbol{y}))}{d[\log(r)]^2}\bigg\vert_{r=\hat{r}}\label{invariance}\\
&=& -\frac{d^2 \log(A(B_j(r(\alpha))\vert \boldsymbol{y}))}{d\alpha^2}\bigg\vert_{\alpha=\hat{\alpha}}\nonumber
\end{eqnarray}

Note that this invariance information is  the negative Hessian value of $\alpha+\log(L(\alpha))$ at the mode $\hat{\alpha}$. Using the invariance information, we  estimate the unconditional posterior variance of shrinkage factor in Equation \ref{admvar} as
\begin{equation}\label{varianceinvariance}
\widehat{Var}(B_j\vert\boldsymbol{y})=\frac{\hat{B}^{\ast2}_j(1-\hat{B}^\ast_j)^2}{inv.info +\hat{B}^\ast_j(1-\hat{B}^\ast_j)}.
\end{equation}

@@

\subsubsection{Unconditional posterior moments of expected random effects}
The Gaussian and Binomial models need to estimate the unconditional posterior moments of expected random effects. We estimate them using their relationship to the conditional posterior moments. For a non-negative constant $c$, the unconditional posterior moments are
\begin{equation}
E((\mu^E_j)^c\vert\boldsymbol{y})=E(E((\mu^E_j)^c\vert A, \boldsymbol{y})\vert\boldsymbol{y})~~\textrm{and}~~E((p^E_j)^c\vert\boldsymbol{y})=E(E((p^E_j)^c\vert r, \boldsymbol{y})\vert\boldsymbol{y}).
\end{equation}
We use the ADM to estimate the conditional posterior moments inside with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in as the estimates of the unconditional moments.
%We estimate the unconditional posterior moments by the estimated conditional posterior moments that we obtain from the conditional posterior distribution of $\mu^E_j\vert A, \boldsymbol{y}$ or that of $p^E_j\vert r, \boldsymbol{y}$ with $\hat{A}=\exp(\hat{\alpha})$ or $\hat{r}=\exp(-\hat{\alpha})$ plugged-in.

To be specific, the ADM for the Binomial model assumes that the conditional posterior distribution of each expected random effect given $\hat{\alpha}$ follows a Beta distribution  because the moment calculation of the expected random effects ($p^E_{1}, p^E_{2}, \ldots p^E_{k}$) involves an intractable integration.  For example, the first conditional posterior moment is
\begin{equation}\label{priormoment1}
E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\boldsymbol{\beta}.
\end{equation}
%We estimate the assumed Beta distribution using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$. We estimate the conditional posterior moments of the expected random effects and treat them as their estimated unconditional posterior moments obtained by the (Laplace) approximate marginal likelihood function of $\boldsymbol{\beta}$.
% The conditional and unconditional posterior moment estimates are almost identical due to the small covariance between $r$ and $\boldsymbol{\beta}$ in the observed information matrix. In addition, calculating the conditional posterior moments is computationally less burdensome. 
%Considering that the expected random effects are a function of logistic regression coefficients $\boldsymbol{\beta}$, we can use the Delta method for the asymptotic Normal distribution of $p^E_{j}(\hat{\boldsymbol{\beta}}_{MLE})$. However, the Normal approximation goes through the same support and boundary issues as the shrinkage factors do. Instead, the ADM assumes that the conditional posterior distribution of $p^E_{j}(\boldsymbol{\beta})$ follows a Beta distribution, using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$.

Thus, we assume the conditional posterior distribution of expected random effect $j$ is a Beta distribution as follows;
\begin{equation}\label{admpriormean}
p^E_{j}\vert\hat{\alpha}, \boldsymbol{y}=\frac{\exp(x_j^\top\boldsymbol{\beta})}{1+\exp(x_j^\top\boldsymbol{\beta})}\bigg\vert\hat{\alpha}, \boldsymbol{y}\sim \textrm{Beta}(b_{1j}, b_{0j})\sim \frac{G(b_{1j})}{G(b_{1j})+G(b_{0j})},
\end{equation}

where $G(b_{1j})$ is a random variable following a Gamma$(b_{1j}, 1)$ distribution with a unit scale and independently $G(b_{0j})$ has a Gamma($b_{0j}, 1)$ distribution.  Note that the representation in Equation \ref{admpriormean} is equivalent to saying $\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables. Its mean and variance are
\begin{eqnarray}
E(\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y})&=&E\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{b_{1j}}{b_{0j}-1}\equiv\eta_j,\label{priormean1}\\
~~~~~Var(\exp(x_j^\top\boldsymbol{\beta})\vert\hat{\alpha}, \boldsymbol{y})&=&Var\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{\eta_j(1+\eta_j)}{b_{0j}-2}.\label{priorvariance1}
\end{eqnarray}

In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ and $\boldsymbol{y}$ follows Normal$(\hat{\beta}, \hat{\Sigma})$ distribution, where $\hat{\boldsymbol{\beta}}$ is the mode of $p(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode. Thus, the posterior distribution of $x_j^\top\boldsymbol{\beta}$ is also Normal with mean $x_j^\top\hat{\boldsymbol{\beta}}$ and variance $x_j^\top\hat{\Sigma} x_j$.

Using the property of the log-Normal distribution for $\exp(x_j^\top\boldsymbol{\beta})$, we estimate the posterior mean and variance in Equation \ref{priormean1} and \ref{priorvariance1} as
\begin{eqnarray}
\hat{\eta}_j&=&\exp(x_j^\top\hat{\boldsymbol{\beta}}+x_j^\top\hat{\Sigma} x_j/2),\label{priormean2}\\
~~~~~\widehat{Var}(\exp(x_j^\top\boldsymbol{\beta})\vert\boldsymbol{y})&=&\hat{\eta}^2_j\big(\exp(x_j^{T}\hat{\Sigma} x_j)-1\big).\label{priorvariance2}
\end{eqnarray}

By matching the  mean and variance in Equation \ref{priormean2} and \ref{priorvariance2} to $b_{1j}$ and $b_{0j}$ in Equation \ref{priormean1} and \ref{priorvariance1}, we estimate the values of $b_{1j}$ and $b_{0j}$ as follows;
\begin{equation}\label{priormeanpara}
\hat{b}_{1j}=\hat{\eta}_j+\frac{\hat{\eta}_j + 1}{\exp(x_j^{T}\hat{\Sigma} x_j)-1}~~\textrm{and}~~\hat{b}_{0j}=\frac{\hat{\eta}_j + 1}{\hat{\eta}_j(\exp(x_j^{T}\hat{\Sigma} x_j)-1)}+2.
\end{equation}

Finally we estimate the unconditional posterior moments of the expected random effects, $E((p^E_{j})^c\vert\boldsymbol{y})$, by $\hat{E}((p^E_{j})^c\vert\hat{\alpha}, \boldsymbol{y})=B(\hat{b}_{1j} + c, \hat{b}_{0j})/B(\hat{b}_{1j}, \hat{b}_{0j})$ for $c\ge0$.
%\begin{equation}\label{priormeanmoments}
%\widehat{E}((p^E_{j})^c\vert\boldsymbol{y})= \frac{B(\hat{b}_{1j} + c, \hat{b}_{0j})}{B(\hat{b}_{1j}, \hat{b}_{0j})}.
%\end{equation}

@@

\subsection{Estimation for random effects}
It is intractable to derive analytically the unconditional posterior distribution of each random effect  for the three models, which motivates us to assume again that each random effect has a skewed Normal distribution \citep{azzalini1985class} for the Gaussian model, a Beta distribution for the Binomial model, or a Gamma distribution for the Poisson model; for $j=1, 2, \ldots, k$,
\begin{eqnarray}
\mu_j\vert\boldsymbol{y} &\sim& \textrm{skewed-Normal}(\phi, \omega, \delta),\label{skewnormal}\\
p_j\vert \boldsymbol{y} &\sim& \textrm{Beta}(t_{1j}, t_{0j}),\label{betapost}\\
\lambda_j\vert \boldsymbol{y} &\sim& \textrm{Gamma}(s_{1j}, s_{0j}).\label{gammapost}
\end{eqnarray}

\cite{kelly2014advances}  matches the  three estimated unconditional posterior  moments of the random effects to the three parameters $(\phi, \omega, \delta$) of the skewed-Normal distribution in Equation \ref{skewnormal}, i.e., location parameter $\phi$, scale parameter $\omega$, and a skewness parameter $\delta$. For this matching, \cite{kelly2014advances} uses $E(\mu_j\vert \boldsymbol{y}) =\phi+\omega\delta\sqrt{2/\pi}$, Var$(\mu_j\vert \boldsymbol{y})=\omega^2(1-2\delta^2/\pi)$, and Skewness$(\mu_j\vert \boldsymbol{y})=(4-\pi)\delta^3/[2(\pi/2-\delta^2)^{3/2}]$ derived in \cite{azzalini1985class}. \cite{kelly2014advances} also shows that the skewed-Normal approximation improves a Normal approximation \citep{tang2011, morris2012} in terms of the frequency properties   of random effects.

@@

 For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimated unconditional posterior mean and variance in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}, respectively, with the estimated unconditional posterior moments of shrinkage factors plugged-in. The estimates of the two parameters $s_{1j}$ and $s_{0j}$ in Equation \ref{gammapost} are
\begin{equation}\label{posttrueprob}
\hat{s}_{1j}=\frac{\hat{\mu}_{\lambda_j}^2}{\hat{\sigma}^2_{\lambda_j}},~\textrm{and}~~\hat{s}_{0j}=\frac{\hat{\mu}_{\lambda_j}}{\hat{\sigma}^2_{\lambda_j}}.
\end{equation}

Finally, the approximate unconditional posterior distribution of random effect $j$ for the Gaussian model is
\begin{equation}\label{trueapprox_normal}
\mu_j\vert \boldsymbol{y} \stackrel{.}{\sim} \textrm{skewed-Normal}(\hat{\phi}, \hat{\omega}, \hat{\delta}),
\end{equation}
that for the Binomial model is
\begin{equation}\label{trueapprox_binomial}
p_j\vert \boldsymbol{y} \stackrel{.}{\sim} \textrm{Beta}(\hat{t}_{1j}, \hat{t}_{0j}),
\end{equation}
and that for the Poisson model is
\begin{equation}\label{trueapprox_poisson}
\lambda_j\vert \boldsymbol{y} \stackrel{.}{\sim} \textrm{Gamma}(\hat{s}_{1j}, \hat{s}_{0j}).
\end{equation}
